---
title: "exercise-09-csu"
author: "Jessica Magalit"
format: html
---
# Question 1:Use the help (?) function to learn more about the dataset

```{r}
data("airquality")
?airquality

```

# Question 2:Use vis_dat to check out the data. Does it need cleaning?

```{r}
library(visdat)
vis_dat(airquality)
clean_airquality <- na.omit(airquality)

```

# Question 3:Fit a linear model to the cleaned data to predict Ozone from one of the possible predictors of your choosing. Why did you chose thats variable?

```{r}
model <- lm(Ozone ~ Solar.R, data = clean_airquality)

```

# Question 4:Using summary(), Does this seem like a valid model?

```{r}
summary(model)

```

# Question 5:Explain the R2 found in a sentence
The model explains only about 12.13% of the variation in ozone levels based on solar radiation, indicating that solar radiation alone is a weak predictor of ozone concentration in this dataset.
```{r}

```

# Question 6:Use broom::augment to predict the Ozone of the cleaned data

```{r}
library(broom)

# Augment the data with fitted values
a <- augment(model, data = clean_airquality)

```

# Question 7:Use ggplot to plot the actual vs predicted Ozone

```{r}
library(broom)
a <- augment(model, data = clean_airquality)
library(ggplot2)

ggplot(a, aes(x = Ozone, y = .fitted)) +
  geom_point() +  # Scatter plot of actual vs predicted
  geom_abline(intercept = 0, slope = 1, color = "red") +  # 1:1 line
  labs(
    title = "Actual vs Predicted Ozone",
    subtitle = paste("Correlation:", round(cor(a$Ozone, a$.fitted), 2))
  ) +
  theme_minimal()

```